An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-27 4_method.tex
b^* => b~, b- or b^

As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
The heights at these elements are then quantized to an integer number of beads.
To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights in between (\cref{sec_central_height_adjustment}).
The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).

@@

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count}.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^*_v = 2 R(v) / w_\text{pref},
\label{eq:initialBeadCount}
\end{equation}
where $w_\text{pref}$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$, also denoted by $b^*$ for short).
Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^*/2$) coincides with a slicing height.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
\jun{I like the information in the last few sentences. Shall we make it short here, and describe them in the slicing subsection.}
%\subsubsection{Initial bead count}\label{sec_initial_bead_count}

@@

\paragraph{Transition anchors}
For a marked edge which connects nodes $v_0$ and $v_1$ with $b^*_{v_0}\le n<b^*_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
% figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
% We call these locations the \emph{transition anchor positions}.
% % Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
To this end, we introduce the function 
\begin{equation}
    q^{-1}(n) := \argmax_d q(d) = n,
\end{equation}
which gives the feature diameter $d$ at which $q$ the bead count transits from $n$ to $n+1$.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
The location of the anchor is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. by
% A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
% We can compute the location of the anchor simply as
\begin{equation}
    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
\end{equation}
%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.

@@

A direct transition from $n$ to $n+1$ beads at an anchor creates sharp turns in the toolpath (see \cref{transitions} top).
A finite transition length ($t(n)$) is designed to ensure a smooth transition (see \cref{transitions} bottom). 
The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
%In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e. where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
%The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
%For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
% A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
% We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
% From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
% For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
The introduction of transition length requires the edge is longer enough to accommodate it. 
%Therefore, if the distance from an anchor to its adjacent node is smaller than $t(n)/2$, the anchor is discarded. 
Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}). 
This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the UoC mesh by adding support edges at transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, in the updated UoC mesh, the marked regions become horizontal at integer multiples of $w_{pref}$ for long stretches with ramps in between.

@@

\begin{algorithm}
\caption{Beading propagation}
\label{alg_beading_propagation}
\begin{algorithmic}
\ForAll{$v \in$ nodes}
	\If {marked($v$)} $\text{map}[v] = (0, B(b^*_v, 2 R(v)))$ \EndIf
\EndFor
\ForAll{$e \in$ edges}
	\If {$R(v_0^e) < R(v_1^e)$}
		% \State 
		upwardEdges.add($e$)
	\EndIf
\EndFor
\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
    		\State $(d, B) = \text{map}[v_0^e]$
    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
	\EndIf
\EndFor
\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
	\If {$\text{map}[v_1^e]$}
    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
    		% d + |v_1^e - v_0^e|
    		\If {$\text{map}[v_0^e]$}
    			\State $(d_0, B_0) = \text{map}[v_0^e]$
    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
    		\EndIf
    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

@@

We then generate extrusion segments for each trapezoid by connecting together the junctions of the same index.
See \cref{segment_generation}.
If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.

>>>>

As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
The heights $b^\sim$ at these elements are then quantized to an integer number of beads $b^\neg$.
To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $b^\wedge$ in between (\cref{sec_central_height_adjustment}).
The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).

@@

%\subsubsection{Union of cones}
\paragraph{Approximation of union of cones}
The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
%In order to visualize the ST as a 3D surface, we add a third dimension.
We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
\begin{equation}
    b^\sim_v = 2 R(v) / w_\text{pref},
\label{eq:initialBeadCount}
\end{equation}
where $w_\text{pref}$ is the nozzle size. 
%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.

@@

\subsection{Central height adjustment}\label{sec_central_height_adjustment}
Now that we have identified and marked the central regions we quantize their heights.
More specifically we round the floating heights ($b^\sim$) to integer bead count values ($b^\neg$).
Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^\sim/2$) coincides with a slicing height.
When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
\jun{I like the information in the last few sentences. Shall we make it short here, and describe them in the slicing subsection.}
%\subsubsection{Initial bead count}\label{sec_initial_bead_count}

@@

\paragraph{Transition anchors}
For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0}\le n<b^\neg_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
% figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
% We call these locations the \emph{transition anchor positions}.
% % Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
To this end, we introduce the function 
\begin{equation}
    q^{-1}(n) := \argmax_d q(d) = n,
\end{equation}
which gives the feature diameter $d$ at which $q$ the bead count transits from $n$ to $n+1$.
%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
The location of the anchor is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. by
% A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
% We can compute the location of the anchor simply as
\begin{equation}
    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
\end{equation}
%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.

@@

A direct transition from $n$ to $n+1$ beads at an anchor creates sharp turns in the toolpath (see \cref{transitions} top).
A finite transition length ($t(n)$) is designed to ensure a smooth transition (see \cref{transitions} bottom). 
The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
%In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e. where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
%The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
%For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
% A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
% We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
% From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
% For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
The introduction of transition length requires the edge is longer enough to accommodate it. 
%Therefore, if the distance from an anchor to its adjacent node is smaller than $t(n)/2$, the anchor is discarded. 
Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}). 
This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the UoC mesh by adding support edges at transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, in the updated UoC mesh, the marked regions become horizontal at integer multiples of $w_{pref}$ for long stretches with ramps in between.

@@

\begin{algorithm}
\caption{Beading propagation}
\label{alg_beading_propagation}
\begin{algorithmic}
\ForAll{$v \in$ nodes}
	\If {marked($v$)} $\text{map}[v] = (0, B(b^\wedge_v, 2 R(v)))$ \EndIf
\EndFor
\ForAll{$e \in$ edges}
	\If {$R(v_0^e) < R(v_1^e)$}
		% \State 
		upwardEdges.add($e$)
	\EndIf
\EndFor
\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
    		\State $(d, B) = \text{map}[v_0^e]$
    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
	\EndIf
\EndFor
\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
	\If {$\text{map}[v_1^e]$}
    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
    		% d + |v_1^e - v_0^e|
    		\If {$\text{map}[v_0^e]$}
    			\State $(d_0, B_0) = \text{map}[v_0^e]$
    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
    		\EndIf
    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
	\EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

@@

We then generate extrusion segments for each trapezoid by connecting together the junctions of the same index.
See \cref{segment_generation}.
If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
If a central edge has both nodes with an odd bead count assigned to it $b^\wedge \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
